---
title: "The Variant Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The Variant Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## How to use the variant package

This vignette will provide a brief overview of how the package is used. 

Let's take an example of two random data frames for which we want to calculate the signal.

```{r setup}
library(variant)

#data frames to check:

df1 <- data.frame(matrix(rnorm(100), ncol = 5))
df2 <- data.frame(matrix(rnorm(1000), ncol = 5))
```


### Checking data frame validity


The first function will check if the data frames are numeric and have an equal number of columns:

```{r}
df_check(df1, df2)
```


### Calculating the correlation matrix

The cormat function calculates the correlation matrix for the data frames:

```{r}
cormat(df1)
```


### Fisher's Transform

The fisher_trans function transforms the r values in the correlation matrix to their respective z-scores:


```{r}
data.frame(lapply(cormat(df1), fisher_trans))
```

### Variant signal

The variant signal will calculate the change on columns whose confidence interval of mean coeff of corr change vs overall change in data frames at a given level of significance. 

```{r}
variant_signal(df1, df2, 0.2)
```



















